Interactive Checks for Coordination Avoidance

### 2019-08-18 doc/vldb_slides/sections/evaluation.tex
Slide tweaks.

  \note{%
    Finally, I'll give a teaser of our evaluation. We implemented our decision
    procedure in Python. You can specify objects, transactions, and invariants
    with code that looks like this.
  }
\end{frame}

@@

  \note{%
    We specified a bunch of examples including things involving foreign keys,
    an auction application, something involving escrow transactions, and TPC-C.
    All the examples verify with a runtime of less then a second and every one
    is implemented in fewer than 75 lines of specification.
  }
\end{frame}

>>>>

  \note{%
    Finally, I'll give a teaser of our evaluation. We implemented our decision
    procedure in Python and leveraged the Z3 decision procedure. You can
    specify objects, transactions, and invariants with code that looks like
    this. \\[12pt]

    This code specifies the running example that we've been looking at
    throughout the talk. $x$ is an integer merged by max that is initially 0.
    $y$ is an integer merged by max that is initially 0. We have a transaction
    incx that increments x and a function decy that decrements y. And, our
    invariant is that the product of $x$ and $y$ is less than or equal to zero.
  }
\end{frame}

@@

  \note{%
    In our paper, we specified a bunch of examples including things involving
    foreign keys, an auction application, something involving escrow
    transactions, and TPC-C.  All the examples verify with a runtime of less
    then a second and every one is implemented in fewer than 75 lines of
    specification.
  }
\end{frame}
